\begin{bibset}{Перечень ссылок}
\begin{thebibliography}{}
    \bibitem{test} 802.11 WLAN Packets and Protocols [Электронный ресурс] / INC WILDPACKETS - Режим доступа : www/ URL:
    http://www.wild packets.com/resources/compendium/wireless\_lan/wlan\_packets/
    \bibitem{test} Stubblefield, A. A Key Recovery Attack on the 802.11b WEP / Stubblefield, A. Ioannidis, J. and Rubin, A. // - 15 с.
    \bibitem{test} Fluhrer, S. Attacks on RC4 and WEP / Fluhrer, S., Mantin, I., Shamir, A. // - 9 с.
    \bibitem{test} Tews, E. Breaking 104 bit WEP in less than 60 seconds / Tews, E., Weinmann, R.-P., Pyshkin, A. // - 2007 - 16 с.
    \bibitem{test} Атаки на WEP [Электронный ресурс] / Сергей Гордейчик - Режим доступа : www/ URL: www.nestor.minsk.by/sr/2007/02/sr70203.html
    \bibitem{test} Roos, A. A Class of Weak Keys in the RC4 Stream Cipher // - 1995 - 8 c.
    \bibitem{test} Goutam, P. On Non-negligible Bias of the First Output Byte of RC4 towards the First Three Bytes of the Secret Key. / Goutam, P., Siddheshwar, R., Subhamoy M. // Proceedings of the International Workshop on Coding and Cryptography - 2007 - 285-294 с.
    \bibitem{test} Goutam, P. Permutation after RC4 Key Scheduling Reveals the Secret Key. / Goutam, P., Subhamoy, M. // SAC - 2007 - 360-377 с.
    \bibitem{test} Souradyuti, P. A New Weakness in the RC4 Keystream Generator and an Approach to Improve the Security of the Cipher / Souradyuti, P., Preneel, B. // FSE - 2004 - 245-259 с.
    \bibitem{test} Klein, A. Attacks on the RC4 stream cipher, Designs, Codes and Cryptography // - 2008 - 269-286 c.
    \bibitem{test} НПАОП 40.1-1.21-98. Правила безпечної експлуатації електроустановок споживачів.
    \bibitem{test} ГОСТ 12,1.019-79 ССБТ. Электробезопасность. Общие требования.
    \bibitem{test} Методичні вказівки до виконання розділу «Охорона праці» у випускних роботах ОКР «бакалавр» усіх форм навчання / Упоряд.: Б.В.Дзюндзюк, В.А.Айвазов, Т.Є.Стиценко. – Харків: ХНУРЕ, 2012. – 28 с.
    \bibitem{test} НПАОП 40.1-1-32-01 Правила будови електроустановок. Електрообладнання спеціальних установок. 
    \bibitem{test} НПАОП 0.00-1.28-10. Правила охорони праці при експлуатації ЕОМ.
    \bibitem{test} НПАОП 0.00-4.12-05. Типове положення про навчання, інструктаж та перевірку знань працівників з питань охорони праці.
    \bibitem{test} НАПБ Б.03.002-2007 Нормы определения категорий помещений, зданий и наружных установок по взрывопожарной и пожарной опасности.
    \bibitem{test} ДБН В.1.1.7-2002. Защита от пожара. Пожарная безопасность объектов строительства.
    \bibitem{test} ДБН В.25-28-2006. Природне і штучне освітлення.
\end{thebibliography}
\end{bibset}
